---
title: "R Consortium R Submission Pilot 3 - Summary Tables and Figures"
author: "Pilot 3 Team"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    latex_engine: pdflatex
header-includes:
- \usepackage{pdfpages}
---

Note : In Pilot 3, following the same approach as Pilot1, different open-source packages were used when generating each of the 4 analysis outputs to test wider use case scenarios. The outputs were formatted differently intentionally to cover different company specific formatting choices.

\newpage

```{r path, echo=FALSE}
path <- list(
  sdtm = "./submission/sdtm",   # Modify path to the sdtm location
  adam = "./submission/adam",    # Modify path to the adam location
  output = "./submission/output"    # Modify path to the output location
)
```

#### Table 14-2.01
#### Summary of Demographic and Baseline Characteristics

```{r demog, out.width = "40%", out.height = "400px", echo=FALSE, message=FALSE, comment=NA}
setwd("/cloud/project") 
source("/cloud/project/submission/programs/tlf-demographic.r")
print(tbl)
```

\newpage

#### Table 14-3.01
#### Primary Endpoint Analysis: ADAS Cog (11) - Change from Baseline to Week 24 - LOCF

```{r primary, echo=FALSE, message=FALSE, comment=NA}
# setwd("/cloud/project")
# source("/cloud/project/submission/programs/tlf-primary.r")
```

\hfill\break\hfill\break\hfill\break\includegraphics[page=1]{/cloud/project/submission/output/tlf-primary-pilot3.rtf.pdf}
\
\


\newpage

#### Table 14-3.02
#### Primary Endpoint Analysis: Glucose (mmol/L) - Summary at Week 20 - LOCF

```{r efficacy, echo=FALSE, message=FALSE, comment=NA}
# setwd("/cloud/project")
# source("/cloud/project/submission/programs/tlf-efficacy.r")
# print(tbl)
```

\includegraphics[page=1]{/cloud/project/submission/output/tlf-efficacy-pilot3.rtf.pdf}

\newpage

#### Figure 14-1
#### Time to Dermatologic Event by Treatment Group
\
\
```{r plot, echo=FALSE, message=FALSE, comment=NA, fig.align="center",out.width="100%"}
setwd("/cloud/project")
source("/cloud/project/submission/programs/tlf-kmplot.r")
print(km)
```


