---
title: "R Consortium R Submission Pilot 3 - Summary Tables and Figures"
author: "Pilot 3 Team"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    latex_engine: xelatex
---

Note : In Pilot 3, following the same approach as Pilot1, different open-source packages were used when generating each of the 4 analysis outputs to test wider use case scenarios. The outputs were formatted differently intentionally to cover different company specific formatting choices.

\newpage

#### Table 14-2.01
#### Summary of Demographic and Baseline Characteristics

```{r demog, echo=FALSE, message=FALSE, comment=NA}
setwd("/cloud/project") 
source("/cloud/project/submission/programs/tlf-demographic.R")
print(tbl)
```

\newpage

#### Table 14-3.01
#### Primary Endpoint Analysis: ADAS Cog (11) - Change from Baseline to Week 24 - LOCF

```{r primary, echo=FALSE, message=FALSE, comment=NA}
setwd("/cloud/project")
source("/cloud/project/submission/programs/tlf-primary.R")
```

\newpage

#### Table 14-3.02
#### Primary Endpoint Analysis: Glucose (mmol/L) - Summary at Week 20 - LOCF

```{r efficacy, echo=FALSE, message=FALSE, comment=NA}
setwd("/cloud/project")
source("/cloud/project/submission/programs/tlf-efficacy.R")
print(tbl)
```

\newpage

#### Figure 14-1
#### Time to Dermatologic Event by Treatment Group
\
\
```{r plot, echo=FALSE, message=FALSE, comment=NA}
setwd("/cloud/project")
source("/cloud/project/submission/programs/tlf-kmplot.R")
print(km)
```


