---
title: "ADAE - Adverse Event Analysis"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
    toc_float: true
---

```{r, echo = FALSE, message = FALSE}
library(admiraldev)
library(haven)
library(readxl)
library(dplyr)
```


The ADSL dataset code can be found [here](https://github.com/RConsortium/submissions-pilot3-adam/blob/main/submission/programs/adae.r)

## Specification File

This was the specification file used to help generate the ADaM.

```{r, echo = FALSE}
adae_spec <- read_xlsx("../submission/adam/ADaM - Pilot 3.xlsx", sheet = 3) %>%
  filter(Dataset == "ADAE")
dataset_vignette(adae_spec)
```

## Dataset

R-generated ADaM


```{r, echo = FALSE}
adae <- read_xpt("../submission/adam/adae.xpt")
dataset_vignette(adae)
```

## QC Findings and Et Cetera

The original ADAE was done in SAS and a quick QC was done.  The code for the comparison between the R and SAS generated datasets can be found [here](https://github.com/RConsortium/submissions-pilot3-adam/blob/main/submission/programs/qc_adae.r)

Differences around the SAS and R generated dataset can be found [here](https://github.com/RConsortium/submissions-pilot3-adam/wiki/QC-Findings#adae) 

