---
title: "Submission Program Preparation"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '2'
    toc_float: true
resource_files:
   - pdf/*.pdf
---

```{r, message = FALSE}
# Initiate start-up file
source(file.path(rprojroot::find_root("DESCRIPTION"), "inst/startup.R"))
```

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(pkglite)
```

# Pack Proprietary R Analysis Package

Using `pkglite` to pack proprietary R package and saved into `ectd/r0pkg.txt`. 

```{r}
path$home %>%
  collate(file_ectd(), file_auto("inst")) %>%
  prune("R/zzz.R") %>%
  pack(output = "ectd/r0pkg.txt")
```
# Prepare Submission Analysis Progam

Transfer Rmarkdown file to `txt` files and saved in `ectd` folder. 

- (optional) Review and remove unecessary information. For example:

```
knitr::include_graphics("pdf/tlf-efficacy.pdf")
```

- (optional) Add header to help reviewer rerun code. For example: 

```
# Note to Reviewer 
# To rerun the code below, please refer ADRG appendix.
# After required package are installed. 
# The path variable needs to be defined by using example code below
#
# path = list(adam = "path/to/esub/analysis/adam/datasets")    	# Modify path to the actual location
# path$outtable = path$outgraph = "."                           # Output saved in current folder
```

```{r, eval = FALSE}
knitr::purl("tlf-demographic.Rmd", output = "ectd/tlf-demographic.r")
knitr::purl("tlf-efficacy.Rmd",    output = "ectd/tlf-efficacy.r")
knitr::purl("tlf-kmplot.Rmd", output = "ectd/tlf-kmplot.r")
knitr::purl("tlf-primary.Rmd", output = "ectd/tlf-primary.r")
```

## List R package for analysis 

```{r}
pkg <- c("pkglite","haven", "dplyr", "tidyr", "emmeans", "r2rtf","rtables", 
         "ggplot2", "cowplot", "visR",
         "Tplyr", "pharmaRTF", "huxtable")

available.packages(contriburl = contrib.url(repos)) %>% 
  data.frame() %>% 
  subset(Package %in% pkg) %>% 
  select(Package, Version, Repository) %>%
  arrange(Package)
```

Proprietary Package 

```{r}
tribble(~ Package, ~ Version, 
        "pilot1wrappers", "0.1.0")
```

# Dry run 

- Install `pilot1wrappers` from `ectd/r0pkg.txt`. 

```{r, eval = FALSE}
pkglite::unpack(input = "ectd/r0pkg.txt", output = tempdir(), install = TRUE)
```

- Rerun other analysis scripts in `ectd`. 

```{r}
list.files("ectd")
```



